---
title: "ML Session Linear Regression"
author: "Ken"
date: "23 September 2018"
output:
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Some Info
I am teaching a course of Fundamentals of Data Visualisation and Statistical Analysis so if you are interested, have a look and ask your manager!
http://www.coe.auckland.ac.nz/

# Linear Regression
Machine learning uses the similar concept but just more complicated and cooler so before we start recognising faces, let's understand some concept!

The main uses of linear regression are:
* Prediction
* Find a relationship between response and explanatory variables

## Equation
$$ y = intercept +  \beta_1 x_1 + ... + \beta_n x_n  + \epsilon $$
$intercept$ is the value when the explanatory Variable is 0. Thus it could be meaningless value when 0 is not appropriate. $\beta$ is the "impact towards y" by having the explanatory variables. And $\epsilon$ is the random variation in the data.

Basically, what it does is finding a line that produce the minimum error in the data set then finding the algebra equation for that line.



## Advertise Data revisited
Let's go back to Daniel's example to understand the linear regression.

```{r message = F }
Sales.df <- read.csv(file.choose(), header = T) #Load Sales.csv data
head(Sales.df) #Fisrt few rows
tail(Sales.df) #Last few rows
```

These codes above are equivalent to the code below in Python.
```{}
import pandas as pd
SalesPyth = pd.read_csv('~/advertising.csv', index_col=0)
SalesPyth.head() # display the first 5 rows
SalesPyth.tail() # display the first 5 rows
```

## Initial Plots
First of all, we check is there are any relationship between Sales and Advertisement.
Remember, if there is no relationship, we cannot predict anything.

```{r Sales.df, echo=T}
plot(Sales~Total.Adv, data = Sales.df,
     main = "Sales VS Total Money Spent on Adv", #Title of plot
     ylab = "Sales", # y label
     xlab = "Total Money Spent" # x label
     )
```

Seems the more they spent on Advertisement, the more Sales they can expect.

## First Analysis
Let's create a model like the one below to explain the relationship between Sale and Advertisement.

$$ y = intercept + \beta_{Adv} x_{Adv} + \epsilon $$
$\beta_{Adv}$ shows the degree of "impact" of advertisement and $x_{Adv}$ represents the amount of money spent on Advertisement.

```{r echo=T}
Sales.lm <- lm(Sales~Total.Adv, data = Sales.df)
summary(Sales.lm)
```

$R^2$ value for this model is `r summary(Sales.lm)$r.squared ` which means we can explain about 75% of sales variation by Total Money Spent on Adv.

Let's see how it looks like in the original plot!

```{r echo=T}
plot(Sales~Total.Adv , data = Sales.df,
     main = "Sales VS Total Money Spent on Adv", #Title of plot
     ylab = "Sales", # y label
     xlab = "Total Money Spent" # x label
)
points(predict(Sales.lm, newdata = data.frame(Total.Adv = sort(Sales.df$Total.Adv)))~sort(Sales.df$Total.Adv),
              lwd = 2, col = "red")
```

What do you think?

## Add more explanatory variables (attributes)
We know that the impact of advertise differs depending on the platform... like below!

```{r echo = F}
plot(Sales~TV , data = Sales.df,
     main = "Sales VS Total Money Spent on TV Adv", #Title of plot
     ylab = "Sales", # y label
     xlab = "Total Money Spent on TV" # x label
)

plot(Sales~Radio , data = Sales.df,
     main = "Sales VS Total Money Spent on Radio Adv", #Title of plot
     ylab = "Sales", # y label
     xlab = "Total Money Spent on Radio" # x label
)

plot(Sales~Newspaper , data = Sales.df,
     main = "Sales VS Total Money Spent on Newspaper Adv", #Title of plot
     ylab = "Sales", # y label
     xlab = "Total Money Spent on Newspaper" # x label
)
```

```{r echo = T}
pairs(Sales.df)
```

Or we can do something like this too.

```{r echo = T, message = F}
library(s20x)
pairs20x(Sales.df)
```

## Fit a new model?
Maybe we can feed some detailed information to the model?

```{r echo = T}
Sales.lm2 <- lm(Sales~ TV + Radio + Newspaper, data = Sales.df) # Modeling part
summary(Sales.lm2) # Show result of the model
```

Since we the result shows Newpaper do not add any significant impact towards the sales, we can drop it from our morel!

```{r echo = T}
Sales.lm2 <- lm(Sales~ TV + Radio, data = Sales.df) # Modeling part
summary(Sales.lm2) # Show result of the model
```

$R^2$ value for this model is `r summary(Sales.lm2)$r.squared ` which means we can explain about 90% of sales variation by TV and Radio Adv!

Slightly better?

Let's see how it looks like in the plot!

```{r echo = F}
plot(Sales~Total.Adv , data = Sales.df,
     main = "Sales VS Total Money Spent on Adv", #Title of plot
     ylab = "Sales", # y label
     xlab = "Total Money Spent" # x label
)
points(predict(Sales.lm2, newdata = Sales.df[, c(1,2)])~Sales.df$Total.Adv, lwd = 2, col = "blue")
```

Not bad, right?

## Adv and Disadv
The advantages of LR:

* Easy to use
* Can explain relationship well
* Can predict well time to time

The disadvantages of LR:

* Not easy to read the output
* Constrained by a p-value (well, not even one but many of them!)
* Model can be very complicated (quadratic term, transformation, and etc...)





